Quantum Bogosort

### 2022-03-08 paper/main.tex
let's hope I didn't just dox myself

% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{minted}
\usepackage{braket}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{hypcap}

@@

\title{Quantum Bogosort}
\author{George Huebner}
\date{December 4, 2021}

\begin{document}
\maketitle

\begin{abstract}
Gag algorithms are a staple of computer science and provide many a good chuckle. Take, for instance, MiracleSort\textsuperscript{\cite{thompson_2013}}, an algorithm that relies on alpha particle emission to cause erroneous bit flips to sort the list:
\begin{minted}{python}
while isSorted(unsorted_list) is False:
    time.sleep(1000)
\end{minted}
Despite their apparent uselessness, joke algorithms provide valuable insight into algorithm design and complexity\textsuperscript{\cite{gruber_holzer_ruepp_2007}}. In this paper we propose an implementation to Quantum Bogosort, one such joke algorithm.
\end{abstract}

@@

It has an average time complexity of $ O((n+1)!) $ and the nondeterministic (traditional) method has an unbounded worst case time complexity for any non-trivial list.

@@

\begin{figure}[h]
    \centering
    \capstart
    \includegraphics[width=0.9\textwidth]{images/resources.png}
    \caption{Circuit depth, width, and total gate count in relation to $i$}
    \label{fig:resources}
\end{figure}
\vspace{10mm}
\noindent With $o = $ \mintinline{python}{bin(n).count('1')}, we have a time complexity of $O(o)$ for many-worlds and $O(o \cdot (n+1)!)$ for Copenhagen.

@@

unsorted_list = [6, 10, 2589, 0, 47, 178, 324]
possibilities = list(permutations(unsorted_list))
unsorted_list.sort()

sorted = tuple(unsorted_list)

@@

    if index is not None:
        if possibilities[index] == sorted:
            break
end = perf_counter()

>>>>

% Useful packages
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{graphicx}
\usepackage{setspace}
\usepackage{minted}
\usepackage{braket}
\usepackage{float}
\usepackage[colorlinks=true, allcolors=blue]{hyperref}
\usepackage{hypcap}
\usepackage{fancyhdr}

@@

\title{Quantum Bogosort}
\author{George Huebner}
\date{March 18, 2022}

\begin{document}
\pagenumbering{gobble}

\begin{titlepage}
\maketitle
\centering
\large Chicago STEM Fair, Computer Science Research, Design Category \\
\vspace{3em}
\huge Sponsor \\
\vspace{1em}
\large Michael Caines \hspace{15em}
\end{titlepage}

{
\hypersetup{hidelinks}
\tableofcontents
}
\pagebreak

\pagestyle{fancy}
\fancyhead[R]{\textit{Quantum Bogosort}, Huebner}
\fancyhead[L]{}

\pagenumbering{arabic}

\begin{abstract}
\noindent Gag algorithms are a staple of computer science and provide many a good chuckle. Take, for instance, MiracleSort\textsuperscript{\cite{thompson_2013}}, an algorithm that relies on alpha particle emission to cause erroneous bit flips to sort a list:
\begin{minted}{python}
while isSorted(unsorted_list) is False:
    time.sleep(1000)
\end{minted}
Despite their apparent uselessness, joke algorithms provide valuable insight into algorithm design and complexity\textsuperscript{\cite{gruber_holzer_ruepp_2007}}. In this paper we propose an implementation to Quantum Bogosort, one such joke algorithm.
\end{abstract}

@@

\noindent It has an average time complexity of $ O((n+1)!) $ and the nondeterministic (traditional) method has an unbounded worst case time complexity for any non-trivial list.

@@

\begin{figure}[h]
    \centering
    \capstart
    \includegraphics[width=0.9\textwidth]{images/resources.png}
    \caption{Circuit depth, width, and total gate count in relation to $i$}
    \label{fig:resources}
\end{figure}
\vspace{10mm}
\noindent With $o = $ \mintinline{python}{bin(n).count('1')}, we have a time complexity of $O(o)$ for many-worlds and $O(o \cdot n!)$ for Copenhagen.

@@

def isSorted(ls):
    if not ls:
        return True

    prev = ls[0]
    for i in ls:
        if i < prev:
            return False
        prev = i
    return True

unsorted_list = [6, 10, 2589, 0, 47, 178, 324]
possibilities = list(permutations(unsorted_list))

@@

    if index is not None:
        if isSorted(possibilities[index]):
            break
end = perf_counter()
